\abstract

Since its discovery in 2012 at the Large Hadron Collider (LHC), efforts have been made to measure and characterize the properties of the Higgs boson. 
Among these efforts have been searches for rare decays of the Higgs predicted by the standard model (SM) of particle physics. 
One such decay is the process \hzg, which has an expected branching fraction of $\mathcal{B}(\PH\to\PZ\gamma) = (1.57 \pm 0.09) \times 10^{-3}$ in the SM, 
assuming a Higgs boson mass of $m_\PH = \mH\GeV$.
This decay mode has not yet been experimentally observed, and its observation and measurement remains an important goal of Higgs physics research at the LHC.
In addition, a measurement of this decay mode at a rate deviating from the SM prediction would provide indirect evidence of new physics beyond the SM. 

This thesis presents a search for \hzg, where $\mathrm{Z}\to\ell^+\ell^-$ with $\ell=\mathrm{e}$ or $\mu$. The search is performed using a sample of proton-proton ($\mathrm{pp}$) collision data at a center-of-mass energy of $13~\mathrm{TeV}$, recorded by the Compact Muon Solenoid experiment at the LHC, corresponding to an integrated luminosity of $138~\mathrm{fb}^{-1}$. 
Events are assigned to mutually exclusive categories, which exploit differences in both event topology and kinematics of distinct Higgs production mechanisms to enhance signal sensitivity. 
To detect a potential signal, fits are performed to the distributions of ${\ell^+\ell^-\gamma}$ invariant mass in each of these categories simultaneously.
The signal strength $\mu$, defined as the product of the cross section and the branching fraction [$\sigma(\mathrm{pp}\to\mathrm{H})\mathcal{B}(\mathrm{H}\to\mathrm{Z}\gamma)$] relative to the SM expectation, is found to be $\mu= 2.4\,\pm0.9$ for $m_\PH = \mH\GeV$. This measurement corresponds to $\sigma(\mathrm{pp}\to\mathrm{H})\mathcal{B}(\mathrm{H}\to\mathrm{Z}\gamma)=0.21\pm0.08~\mathrm{pb}$. The statistical significance of the observed excess of events is $2.7$ standard deviations. The observed (expected) upper limit at $95$\% confidence level on $\mu$ is $4.1$\,($1.8$). 
The ratio of branching fractions $\mathcal{B}(\mathrm{H}\to\mathrm{Z}\gamma)/\mathcal{B}(\mathrm{H}\to\gamma\gamma)$ is measured to be $1.5^{+0.7}_{-0.6}$, which agrees with the SM prediction at the 
$1.5$ standard deviation level. 
